Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
Add average node degree
revise node labeling

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to a node labeling function $\ell$ such that nodes with similar degrees are assigned the same label. It is due to the assumption that nodes with similar degrees tend to share common properties. Following is the definition of the the function:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq 5 \\
		6+i,\ & \mbox{if }  5 + \left[ \frac{d(G) - 5}{\lambda-5} \right] *i \leq d(u) < 5 + \left[ \frac{d(G) - 5}{\lambda-5}\right] *(i+1)
	\end{array}
\right.$,
\end{center}
where $\lambda > 5$ is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.

@@

\section{Experiment}
In this section, we intend to measure the performance of our proposed method and compare it with other link prediction methods. We follow the procedure used in \cite{matrix-factorization} which employs six datasets in different domains. In the following we shortly describe each dataset.
\begin{itemize}
\item \textit{Protein }\cite{protein-protein}: the medium confidence network which encodes the interaction between proteins. It contains 2617 nodes and 11855 links.

\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links.

\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from the first to the $12^{th}$ edition. Nodes are authors and links encode co-author relation between authors. This network contains 2865 nodes and 4733 links.

\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links.

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between 130 countries. A link connecting two nodes (countries) if they dispute. We have 180 links in total in this network.

\item \textit{Powergrid} cite{powergrid}: a network of electric powergrid in US. It has 4941 nodes and 6594 links.
\end{itemize}

>>>>

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose to a node labeling function $\ell$ which assigns labels for nodes based on node degrees. Our idea is that nodes having small degree, less than or equal to 5, we use the degree values as their labels. For nodes with degree greater than 5, we group them into different groups based on the degrees, nodes are in the same group are assigned the same labels. We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties. Formally, the function is defined as:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq 5 \\
		6+i,\ & \mbox{if }  5 + \left[ \frac{d(G) - 5}{\lambda-5} \right] *i \leq d(u) < 5 + \left[ \frac{d(G) - 5}{\lambda-5}\right] *(i+1)
	\end{array}
\right.$,
\end{center}
where $\lambda > 5$ is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.

@@

\section{Experiment}
In this section, we intend to measure the performance of our proposed method and compare it with other link prediction methods. We follow the procedure used in \cite{matrix-factorization} which employs six datasets in different domains. In the following we shortly describe each dataset.
\begin{itemize}
\item \textit{Protein }\cite{protein-protein}: the medium confidence network which encodes the interaction between proteins. It contains 2617 nodes and 11855 links. The average degree is 9.1.

\item \textit{Metabolic} \cite{metabolic}: a biological network which relates enzyme proteins and chemical compounds and it includes 668 nodes and 2782 links. The average degree is 8.3.

\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from the first to the $12^{th}$ edition. Nodes are authors and links encode co-author relation between authors. This network contains 2865 nodes and 4733 links. The average degree is 3.3.

\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links. The average degree is 0.17.

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between 130 countries. A link connecting two nodes (countries) if they dispute. We have 180 links in total in this network. The average degree is 2.5.

\item \textit{Powergrid} cite{powergrid}: a network of electric powergrid in US. It has 4941 nodes and 6594 links. The average degree is 2.7.
\end{itemize}
